---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ouhr

<!-- badges: start -->
<!-- badges: end -->

The goal of ouhr is to provide useful functions for completing routine procedures. This includes various functions to manipulate dates, e.g., finding financial years or the first of the month, functions for sending emails and functions for creating Excel files.

## Installation

You can install the development version of ouhr like so:

``` {r installing OUHR}
devtools::install_github("AnyaJade/OUHR/ouhr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ouhr)

first_of_month(as.Date("2023-03-28"))
```

# Functions

Below is a list of all the functions currently in ouhr and a summary of what they do.

## Date Manipulations

```{r financial year}
# A function to find the financial year of a given date
financial_year(as.Date("2023-03-28"))
```

```{r first of the month}
# A function to find the first of the month of a given date
first_of_month(as.Date("2023-03-28"))
```

```{r last sunday}
# A function to find the date of the last Sunday before a given date
last_sunday(as.Date("2023-03-28"))
```

```{r previous month}
# A function to find the previous month of a given date
previous_month(as.Date("2023-03-28"))
```

```{r month year}
# A function to create a string of the month and year where month can be either the full name, abbreviated or a number in MM format
monthyear(as.Date("2023-03-28"), "abb")
monthyear(as.Date("2023-03-28"), "full")
monthyear(as.Date("2023-03-28"), "num")
```

```{r month zero}
# A function to convert a month into "MM" format
month_zero(as.Date("2023-03-28"))
```

## Email

```{r email}
# A function to create an email
email(To = "anya.ferguson@ouh.nhs.uk; EDandSupportServicesInformationTeam@oxnet.nhs.uk",
      Cc = "example@ouh.nhs.uk",
      subject = "Testing email function from OUHR package",
      body = "Testing the email function from OUHR package. <p> Please ignore this email."
      )
```

```{r email with table}
library(tidyverse)
library(kableExtra)

# Can also add a table to an email body, or an attachment
cars_table <- cars %>% 
  kable(booktabs = TRUE) %>% 
  kable_styling(full_width = F)

email(To = "anya.ferguson@ouh.nhs.uk; EDandSupportServicesInformationTeam@oxnet.nhs.uk",
      body = "Testing the email function from OUHR package.",
      table = cars_table,
      body2 = "The table above shows the cars dataset."
      )
```

```{r email for information requests}
# A function to create 1 of 4 emails specifically for information requests
email_info_request(type = "password",
                   To = "anya.ferguson@ouh.nhs.uk ",
                   dear = "Anya",
                   password = "test"
                   )
```

## Excel
```{r saving excel}
# A function to save excel, with option to add a password
wb <- openxlsx::createWorkbook()

openxlsx::addWorksheet(wb, "example")

save_excel(wb = wb, 
           filename = "C:/examplewithpassword.xlsx", 
           password = "test"
           )
```

```{r plot in excel}
# A function to add a plot to excel
plot1 <- plot(cars)

wb1 <- openxlsx::createWorkbook()

openxlsx::addWorksheet(wb1, "example")

plot_excel(wb = wb1,
           sheetname = "example", 
           plot = plot1,
           plot_position = c(5, 3),
           plot_width = 10
           )

save_excel(wb = wb1, 
           filename = "C:/exampleplot.xlsx"
           )
```

```{r one table only in excel}
# A function to create an excel file with data saved in only one table in only one sheet
one_table_excel(sheetname = "data", 
                data = cars, 
                filename = "C:/exampletable.xlsx", 
                column_widths = c(5, 8), 
                columns = c(1, 2)
                )
```

```{r one table per group in excel}
# A function to add one sheet per group in an excel sheet, each with one table. 
wb <- openxlsx::createWorkbook()

data <- cars %>% mutate("speed_category" = ifelse(speed <15, "Less than 15", "Greater than 15"))

group_table_excel(wb = wb1, data = data, group = speed_category, range = c("Less than 15", "Greater than 15"))

save_excel(wb = wb, 
           filename = "C:/examplegroup.xlsx"
           )
```

```{r deleting data from excel}
# A function to delete all data from a start row and start col to end of excel sheet
one_table_excel(data = cars, filename = "C:/example.xlsx")

wb <- openxlsx::loadWorkbook("C:/example.xlsx")

delete_all_excel(template = "C:/example.xlsx", wb = wb, sheet = "Sheet1", row_start = 5)

save_excel(wb = wb, filename = "C:/example.xlsx")
```


## Other
```{r random password}
# A function to create a string of upper/lower case letters and numbers of a desired length, with option to specify a seed.
random_password(seed = 1, length = 4)
```

```{r prescriptions}
# A function to create a base SQL query that searches columns CATALOG_CD_DISPLAY, ORDER_MNEMONIC and ORDERED_AS_MNEMONIC in TDWH_ORH.WareHouse.ODS.d_PrescriptionOrders for all provided drugs in a specified date range
prescriptions(drugs = c("Berinert", "Cinryze", "Orladeyo"), 
              startdate = "2023-06-01", 
              enddate = "2023-06-30"
              )
```

```{r reading in .sql files}
# A function to read .sql files into R. 
filename <- "C:/SVN/R/Testing read_sql function.sql"
read_sql(filename)
```



