---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ouhr

<!-- badges: start -->
<!-- badges: end -->

The goal of ouhr is to provide useful functions for completing routine procedures. This includes various functions to manipulate dates, e.g., finding financial years or the first of the month, functions for sending emails and functions for creating Excel files.

## Installation

You can install the development version of ouhr like so:

``` {r installing OUHR, eval = FALSE}
devtools::install_github("AnyaJade/OUHR/ouhr")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(ouhr)

first_of_month(as.Date("2023-03-28"))
```

# Functions

Below is a list of all the functions currently in ouhr and a summary of what they do.

## Date Manipulations
+ `financial_month()` for getting the financial month from a date.
+ `financial_year()` for getting the	Financial Year from a date.
+ `first_of_month()` for getting the	First of the Month from a date.
+ `last_sunday()` for getting the	Last Sunday from a date.
+ `monthyear()` for getting the Month and Year from a date in 1 of 3 formats.
+ `month_zero()` for adding a zero to month.
+ `previous_month()` for 	Previous Month from a date.

## Email
+ `email()` for creating an Email.
+ `email_info_request()` for creating emails for info requests.

## Excel
+ `delete_all_excel()` for deleting existing data from an Excel sheet.
+ `group_table_excel()` for adding one sheet and table per group to Excel.
+ `one_table_excel()` for creating and Excel file with one table.
+ `plot_excel()` for adding a plot to Excel.
+ `save_excel()` for saving an Excel File with optional password.

## SQL
+ `append_sql()` for appending data to SQL.
+ `match_data()` for matching data.
+ `prescriptions()` for writing a prescriptions SQL query.
+ `read_sql()` for reading .sql files.
+ `unmatched_names()` for finding unmatched names.

## Other
+ `random_password()` for generating random strings.
+ `wrap_up()` for	wrap up of scripts.


